Stage-structured evolutionary demography for simultaneous hermaphrodites with partial selfing

### 2020-07-09 notes/notes-SA-partSelf-wDemography.tex
added warning to notes about coexistence conditions
Update notes-SA-partSelf-wDemography.tex
Calculated the coexistence conditions for the general case (when how-you-were-produced matters), checked they reduce to deVries&Caswell (2019, AmNat) in the absence of selfing. Then formulated model and calculated coexistence conditions when how-you-were-produced does not affect your survival.

% Definitions
\def\mathbi#1{\textbf{\em #1}}
\def\mbf#1{\mathbf{#1}}
\def\mbb#1{\mathbb{#1}}
\def\mcal#1{\mathcal{#1}}

@@

@@

\begin{equation}
	\mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{p} = 
		\left(
			\begin{array}{ccc}
				\mbf{1}^{\intercal}_{\omega} & \frac{1}{2} \mbf{1}^{\intercal}_{\omega} & 0 \\
				0 & \frac{1}{2} \mbf{1}^{\intercal}_{\omega} & \mbf{1}^{\intercal}_{\omega} \\
			\end{array} \right)
		\left(
			\begin{array}{ccc}
				\mbf{F}^{\prime}_{AA} & 0 & 0 \\
				0 & \mbf{F}^{\prime}_{Aa} & 0 \\
				0 & 0 & \mbf{F}^{\prime}_{aa} \\
			\end{array} \right)
		\left(
			\begin{array}{c}
				\mbf{p}_{AA} \\
				\mbf{p}_{Aa} \\
				\mbf{p}_{aa} \\
			\end{array} \right)
\end{equation}

\noindent The matrix $\mbb{F}^{\prime}$ operates on the vector of genotype frequencies to give the relative contributions of each genotype to the male gamete pool. The matrix $\mbf{W}^{\prime}$ converts these relative genotype contributions to allele numbers. Normalizing this vector gives the allele frequencies in the gamete pool,

\begin{equation} \label{eq:maleGametePool}
	\left(
		\begin{array}{c}
			q^{\prime}_{A} \\
			q^{\prime}_{a} \\
		\end{array} \right) = 
			\frac{\mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{p}}{\| \mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{p} \|} = 
				\frac{\mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{n}}{\| \mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{n} \|}
\end{equation}

@@

\begin{align*}
	&\tilde{\mbf{A}}[\tilde{\mbf{n}}] = 
		 \underbrace{\left(
			\begin{array}{ccc|ccc}
				\mcal{U}^S_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{AA} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{aa} & \mbf{0}\\
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{aa}
			\end{array} \right)}_{\tilde{\mbf{U}}} + \\ 
	&\underbrace{\left(
			\begin{array}{ccc|ccc}
				C_{AA} (1 - \delta) \mbf{F}_{AA} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & C_{AA} (1 - \delta) \mbf{F}_{AA} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} \\ 
				\mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0}  \\
				\mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} \\ \hline
				q^{\prime}_{A} \mbf{F}_{AA} (1 - C_{AA})& \frac{1}{2} q^{\prime}_{A} \mbf{F}_{Aa} (1 - C_{Aa}) & \mbf{0} & q^{\prime}_{A} \mbf{F}_{AA} (1 - C_{AA})& \frac{1}{2} q^{\prime}_{A} \mbf{F}_{Aa} (1 - C_{Aa}) & \mbf{0} \\
				q^{\prime}_{a} \mbf{F}_{AA} (1 - C_{AA}) & \frac{1}{2} \mbf{F}_{Aa} (1 - C_{Aa}) & q^{\prime}_{A} \mbf{F}_{aa} (1 - C_{aa}) & q^{\prime}_{a} \mbf{F}_{AA} (1 - C_{AA}) & \frac{1}{2} \mbf{F}_{Aa} (1 - C_{Aa}) & q^{\prime}_{A} \mbf{F}_{aa} (1 - C_{aa}) \\
				\mbf{0} & \frac{1}{2} q^{\prime}_{a} \mbf{F}_{Aa} (1 - C_{Aa})& q^{\prime}_{a} \mbf{F}_{aa} (1 - C_{aa}) & \mbf{0} & \frac{1}{2} q^{\prime}_{a} \mbf{F}_{Aa} (1 - C_{Aa})& q^{\prime}_{a} \mbf{F}_{aa} (1 - C_{aa})
			\end{array} \right)}_{\tilde{\mbf{F}}} \numberthis
\end{align*}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Coexistence conditions}
\setcounter{equation}{0}

@@

\begin{equation}
	\tilde{\mbf{n}} = \left(
			\begin{array}{c}
							\mbf{n}_{AA} \\
							\mbf{n}_{AA} \\ \hline
							\mbf{n}_{Aa} \\
							\mbf{n}_{Aa} \\ \hline
							\mbf{n}_{aa} \\
							\mbf{n}_{aa} \\
			\end{array} \right).
\end{equation}

\noindent Note that to 'doubling' up of the genotype-specific vectors in each block is done out of convenience, because the population projection matrix is organized around two sex-functions.

@@

\begin{align*} \label{eq:AtildeCoexistence}
	\tilde{\mbf{A}}[\tilde{\mbf{n}}] &= \tilde{\mbf{U}} + \tilde{\mbf{F}} \\
		&= \left(
			\begin{array}{cc|cc|cc}
				\mcal{U}^S_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{0} & \mcal{U}^X_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\\hline
				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa} & \mbf{0} &  \mbf{0}\\\hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa}
			\end{array} \right) \\ 
		&+ \left(
			\begin{array}{cc|cc|cc}
				C_{AA} (1 - \delta) \mbf{F}_{AA} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				q^{\prime}_{A} \mbf{F}_{AA} (1 - C_{AA}) & \mbf{0} & \frac{1}{2} q^{\prime}_{A} \mbf{F}_{Aa} (1 - C_{Aa}) & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\
				q^{\prime}_{a} \mbf{F}_{AA} (1 - C_{AA}) & \mbf{0} & \frac{1}{2} \mbf{F}_{Aa} (1 - C_{Aa}) & \mbf{0} & q^{\prime}_{A} \mbf{F}_{aa} (1 - C_{aa}) & \mbf{0}\\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & C_{aa} (1 - \delta) \mbf{F}_{aa} & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \frac{1}{2} q^{\prime}_{a} \mbf{F}_{Aa} (1 - C_{Aa})  & \mbf{0} & q^{\prime}_{a} \mbf{F}_{aa} (1 - C_{aa}) & \mbf{0}
			\end{array} \right) \numberthis
\end{align*}

@@

The two-sex Mendelian matrix model defined by above reduces to a linear matrix model on the boundary where the population is initially fixed for the $A$ allele (since $q^{\prime}_{A} = 1$ and $q^{\prime}_{a} = 0$). Provided the initial population contains a nonzero number of females, the population will grow or shrink exponentially after converging to a stable population structure (see Caswell (2001), section 4.5.2.1). We can take advantage of the homogeneity of $\tilde{\mbf{F}}$, we rewrite the model in terms of the normalized population vector (the frequency vector):

@@

\begin{align*}
	\mbf{B}[\hat{\mbf{p}}] &= \frac{ \tilde{\mbf{A}}[\hat{\mbf{p}}] }{ \mbf{1}^{\intercal}_{\omega g} \tilde{\mbf{A}}[\hat{\mbf{p}}] \hat{\mbf{p}} } = \\
						   \frac{1}{\lambda_{AA}} &
						   \left(
			\begin{array}{cc|cc|cc}
				\mcal{U}^S_{AA} + C_{AA} (1 - \delta) \mbf{F}_{AA} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{F}_{AA} (1 - C_{AA}) & \mcal{U}^X_{AA} & \frac{1}{2} \mbf{F}_{Aa} (1 - C_{Aa}) & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} + \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \frac{1}{2} \mbf{F}_{Aa} (1 - C_{Aa}) & \mcal{U}^X_{Aa} & \mbf{F}_{aa} (1 - C_{aa}) & \mbf{0}\\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mcal{U}^S_{aa} + C_{aa} (1 - \delta) \mbf{F}_{aa} & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \mbf{0}  & \mbf{0} & \mbf{0} & \mcal{U}^X_{aa}
			\end{array} \right) \numberthis
\end{align*}

@@

\begin{equation}
	\encircle{B} = - \frac{1}{\lambda_{AA}} \left( \hat{\mbf{p}}^{\intercal} \otimes \mbf{1}_{2 \omega g} \right) \left( \text{vec} \tilde{\mbf{A}} \right) \left( \mbf{1}^{\intercal}_{2 \omega g} \tilde{\mbf{A}} \right).
\end{equation}

@@

>>>>

% Definitions
\def\mathbi#1{\textbf{\em #1}}
\def\mbf#1{\mathbf{#1}}
\def\mbb#1{\mathbb{#1}}
\def\mcal#1{\mathcal{#1}}
\newcommand{\bo}[1]{{\bf #1}}
\newcommand{\tr}{{\mbox{\tiny \sf T}}}

\newcommand{\bm}[1]{\mbox{\boldmath $#1$}}

@@

\hl{We have to be a bit careful with our notation. Above we have defined $\mathbf{n}^X$ as the population vector of individuals that were produced by selfing, so it would be natural to use $\mathbf{p}^X$ as the normalized version of that vector, which is in conflict with the above definition of $\mbf{p^X_i} $.}

@@

\begin{equation}
	\mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{p} = 
		\left(
			\begin{array}{ccc}
				\mbf{1}^{\intercal}_{\omega} & \frac{1}{2} \mbf{1}^{\intercal}_{\omega} & 0 \\
				0 & \frac{1}{2} \mbf{1}^{\intercal}_{\omega} & \mbf{1}^{\intercal}_{\omega} \\
			\end{array} \right)
		\left(
			\begin{array}{ccc}
				\mbf{F}^{\prime}_{AA} & 0 & 0 \\
				0 & \mbf{F}^{\prime}_{Aa} & 0 \\
				0 & 0 & \mbf{F}^{\prime}_{aa} \\
			\end{array} \right)
		\left(
			\begin{array}{c}
				\mbf{p}_{AA} \\
				\mbf{p}_{Aa} \\
				\mbf{p}_{aa} \\
			\end{array} \right)
\end{equation}
\hl{This vector has to be created from a sum of $\mathbf{n}^X$ and $\mathbf{n}^S$ since they both outcross.}

\noindent The matrix $\mbb{F}^{\prime}$ operates on the vector of genotype frequencies to give the relative contributions of each genotype to the male gamete pool. The matrix $\mbf{W}^{\prime}$ converts these relative genotype contributions to allele numbers. Normalizing this vector gives the allele frequencies in the gamete pool (\textbf{is it worth emphasizing here that this is frequencies in pollen?}),

\begin{equation} \label{eq:maleGametePool}
	\left(
		\begin{array}{c}
			q^{\prime}_{A} \\
			q^{\prime}_{a} \\
		\end{array} \right) = 
			\frac{\mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{p}}{\| \mbf{W}^{\prime} \mbb{F}^{\prime} \mbf{p} \|} = 
				\frac{\mbf{W}^{\prime} \mbb{F}^{\prime} (\mbf{n}^X+ \mbf{n}^S)}{\| \mbf{W}^{\prime} \mbb{F}^{\prime} (\mbf{n}^X+ \mbf{n}^S)\|}
\end{equation}

@@

\begin{align*}
	&\tilde{\mbf{A}}[\tilde{\mbf{n}}] = 
		 \underbrace{\left(
			\begin{array}{ccc|ccc}
				\mcal{U}^S_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{AA} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{aa} & \mbf{0}\\
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{aa}
			\end{array} \right)}_{\tilde{\mbf{U}}} + \\ 
	&\underbrace{\left(
			\begin{array}{ccc|ccc}
				C_{AA} (1 - \delta) \mbf{F}_{AA} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & C_{AA} (1 - \delta) \mbf{F}_{AA} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} \\ 
				\mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0}  \\
				\mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} \\ \hline
				q^{\prime}_{A} (1 - C_{AA})\mbf{F}_{AA} & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \mbf{0} & q^{\prime}_{A} (1 - C_{AA}) \mbf{F}_{AA}& \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa}) \mbf{F}_{Aa} & \mbf{0} \\
				q^{\prime}_{a} (1 - C_{AA}) \mbf{F}_{AA} & \frac{1}{2} (1 - C_{Aa})\mbf{F}_{Aa}  & q^{\prime}_{A} (1 - C_{aa})\mbf{F}_{aa}  & q^{\prime}_{a} (1 - C_{AA}) \mbf{F}_{AA} & \frac{1}{2}(1 - C_{Aa}) \mbf{F}_{Aa}  & q^{\prime}_{A} (1 - C_{aa})\mbf{F}_{aa}  \\
				\mbf{0} & \frac{1}{2} q^{\prime}_{a} (1 - C_{Aa})\mbf{F}_{Aa} & q^{\prime}_{a} (1 - C_{aa}) \mbf{F}_{aa} & \mbf{0} & \frac{1}{2} q^{\prime}_{a} (1 - C_{Aa})\mbf{F}_{Aa} & q^{\prime}_{a} (1 - C_{aa})\mbf{F}_{aa} 
			\end{array} \right)}_{\tilde{\mbf{F}}} \numberthis
\end{align*}

@@

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Coexistence conditions}
\setcounter{equation}{0}
%\hl{EVERYTHING BELOW THIS POINT IS JUNK, AS IT HAS NOT BEEN UPDATED WITH THE NEW $\tilde{\mbf{A}}$ structure!!!}

@@

\begin{equation}
	\tilde{\mbf{n}} = \left(
			\begin{array}{c}
							\mbf{n}^S_{AA} \\
							\mbf{n}^X_{AA} \\ \hline
							\mbf{n}^S_{Aa} \\
							\mbf{n}^X_{Aa} \\ \hline
							\mbf{n}^S_{aa} \\
							\mbf{n}^X_{aa} \\
			\end{array} \right).
\end{equation}

\noindent Note that we are still keeping track of whether individuals were produced through selfing, $\mbf{n}^S_{ij}$, or through outcrossing, $\mbf{n}^X_{ij}$ [\textit{\textbf{LdV: I'm not a fan of combining superscripts and subscripts because it becomes such a mess of indices, what if we give them different letters instead, e.g. $\mbf{n}^S_{AA}=\mbf{n}_{AA}$ and $\mbf{n}^X_{AA}=\mbf{m}_{AA}$?}}].

@@

{
\small
\begin{align*} \label{eq:AtildeCoexistence}
	\tilde{\mbf{A}}[\tilde{\mbf{n}}] &= \tilde{\mbf{U}} + \tilde{\mbf{F}}\\
		&= \left(
			\begin{array}{cc|cc|cc}
				\mcal{U}^S_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{0} & \mcal{U}^X_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\\hline
				\mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa} & \mbf{0} &  \mbf{0}\\\hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^S_{Aa} & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mcal{U}^X_{Aa}
			\end{array} \right) \\ 
		&+ \left(
			\begin{array}{cc|cc|cc}
				C_{AA} (1 - \delta) \mbf{F}_{AA} & C_{AA} (1 - \delta) \mbf{F}_{AA}  & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \mbf{0} & \mbf{0} \\ 
				q^{\prime}_{A}  (1 - C_{AA}) \mbf{F}_{AA}& q^{\prime}_{A} (1 - C_{AA}) \mbf{F}_{AA} & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \frac{1}{2} q^{\prime}_{A} (1 - C_{Aa})\mbf{F}_{Aa}  & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}& \mbf{0} & \mbf{0} \\
				q^{\prime}_{a} (1 - C_{AA}) \mbf{F}_{AA} & q^{\prime}_{a}(1 - C_{AA})  \mbf{F}_{AA} & \frac{1}{2}  (1 - C_{Aa}) \mbf{F}_{Aa}& \frac{1}{2} (1 - C_{Aa})\mbf{F}_{Aa} & q^{\prime}_{A} (1 - C_{aa})\mbf{F}_{aa}  & q^{\prime}_{A}  (1 - C_{aa})\mbf{F}_{aa}\\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & C_{aa} (1 - \delta) \mbf{F}_{aa} &  C_{aa} (1 - \delta) \mbf{F}_{aa}\\ 
				\mbf{0} & \mbf{0} & \frac{1}{2} q^{\prime}_{a}  (1 - C_{Aa}) \mbf{F}_{Aa} & \frac{1}{2} q^{\prime}_{a}  (1 - C_{Aa})\mbf{F}_{Aa}& q^{\prime}_{a}(1 - C_{aa})  \mbf{F}_{aa} & q^{\prime}_{a} (1 - C_{aa})\mbf{F}_{aa} 
			\end{array} \right) \numberthis
\end{align*}
}

@@

The Mendelian matrix model defined by above reduces to a linear matrix model on the boundary where the population is initially fixed for the $A$ allele (since $q^{\prime}_{A} = 1$ and $q^{\prime}_{a} = 0$). Provided the initial population contains a nonzero number of females, the population will grow or shrink exponentially after converging to a stable population structure (see Caswell (2001), section 4.5.2.1). We can take advantage of the homogeneity of $\tilde{\mbf{F}}$, we rewrite the model in terms of the normalized population vector (the frequency vector):

@@

\begin{align*}
	\mbf{B}[\hat{\mbf{p}}] &= \frac{ \tilde{\mbf{A}}[\hat{\mbf{p}}] }{ \mbf{1}^{\intercal}_{\omega g} \tilde{\mbf{A}}[\hat{\mbf{p}}] \hat{\mbf{p}} } = \\
						   \frac{1}{\lambda_{AA}} &
						   \left(
			\begin{array}{cc|cc|cc}
				\mathbf{U}^S_{AA} & \mbf{0}& \mbf{0} & \mbf{0} & \mbf{0} \\ 
			\mbf{0} & \mathbf{U}^X_{AA} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \mathbf{U}^S_{Aa}& \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0}& \mcal{U}^X_{Aa} & \mbf{0} & \mbf{0}\\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mathbf{U}^S_{aa}  & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \mbf{0}  & \mbf{0} & \mbf{0} & \mathbf{U}^X_{aa}
			\end{array} \right) \\
			 +\frac{1}{\lambda_{AA}} &
						   \left(
			\begin{array}{cc|cc|cc}
		 C_{AA} (1 - \delta) \mbf{F}_{AA} & C_{AA} (1 - \delta) \mbf{F}_{AA}& \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}& \mbf{0} & \mbf{0} \\ 
				(1 - C_{AA}) \mbf{F}_{AA} & (1 - C_{AA}) \mbf{F}_{AA}  & \frac{1}{2}(1 - C_{Aa}) \mbf{F}_{Aa}  & \frac{1}{2} (1 - C_{Aa})\mbf{F}_{Aa} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{2} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} & \frac{1}{2} (1 - C_{Aa}) \mbf{F}_{Aa} & (1 - C_{aa}) \mbf{F}_{aa} & (1 - C_{aa}) \mbf{F}_{aa}\\ \hline
				\mbf{0} & \mbf{0} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa} & \frac{1}{4} C_{Aa} (1 - \delta) \mbf{F}_{Aa}  &C_{aa} (1 - \delta) \mbf{F}_{aa} &C_{aa} (1 - \delta) \mbf{F}_{aa} \\ 
				\mbf{0} & \mbf{0} & \mbf{0}  & \mbf{0} & \mbf{0} &\mbf{0}
			\end{array} \right) 
			\numberthis
\end{align*}

@@

\begin{equation}
	\encircle{B} = - \frac{1}{\lambda_{AA}^2} \left( \hat{\mbf{p}}^{\intercal} \otimes \mbf{1}_{2 \omega g} \right) \left( \text{vec} \tilde{\mbf{A}} \right) \left( \mbf{1}^{\intercal}_{2 \omega g} \tilde{\mbf{A}} \right).
\end{equation}

@@

\begin{equation}
	\encircle{B} = - \frac{1}{\lambda_{AA}} \hat{\mbf{p}} \left( \mbf{1}^{\intercal}_{2 \omega g} \tilde{\mbf{A}}[\hat{\mbf{p}}] \right).
\end{equation}

\begin{equation}
	\hat{\mbf{p}} = \left(
			\begin{array}{c}
							\hat{\mbf{p}}^S_{AA} \\
							\hat{\mbf{p}}^X_{AA} \\ \hline
							0                  \\
							0                  \\ \hline
							0                  \\
							0                  \\
			\end{array} \right)
\end{equation}

\begin{landscape}
\noindent and rewrite in terms of the block matrices to obtain

{\footnotesize
\begin{align*}
	\encircle{B} =& \\
	&-\frac{1}{\lambda_{AA}} \left(
			\begin{array}{cc|cc|cc}
				\hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^S_{AA} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^X_{AA} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^S_{Aa} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^X_{Aa} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^S_{aa} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^X_{aa} \\ 
				\hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^S_{AA} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^X_{AA} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^S_{Aa} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^X_{Aa} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^S_{aa} & \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{U}^X_{aa} \\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} 
			\end{array} \right) \\
	&-\frac{1}{\lambda_{AA}} \left(
			\begin{array}{cc|cc|cc}
				(1 - \delta C_{AA}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{AA} & (1 - \delta C_{AA}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{AA} & (1 - \delta C_{Aa}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{Aa} & (1 - \delta C_{Aa}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{Aa}  & (1 - \delta C_{aa}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{aa} & (1 - \delta C_{aa}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{aa} \\ 
				 	(1 - \delta C_{AA}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{AA} & 	(1 - \delta C_{AA}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{AA} & (1 - \delta C_{Aa})  \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{Aa} & (1 - \delta C_{Aa})  \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{Aa} & (1 - \delta C_{aa}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{aa} & (1 - \delta C_{aa}) \hat{\mbf{p}}_{AA} \otimes \mbf{1}^{\intercal}_{\omega} \mbf{F}_{aa}\\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ \hline
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} \\ 
				\mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0} & \mbf{0}
			\end{array} \right) \\
			 \numberthis			
\end{align*}
}

\textit{\textbf{Oof, I realized in doing this that I made a mistake here in the appendix of the two sex paper, the alpha's should have disappeared because when you sum over all the rows they cancel. }}

Finally, we turn to term \encircle{C} of the Jacobian. As far as I can tell, we can follow the steps leading from Eq(A-35) through to Eq(A-46) of de Vries \& Caswell (2019) Appendix A exactly because the structure of our $\tilde{\mbf{A}}$ equations are identical. We resume the derivation at our version of their Eq(A-47)...Substitute $\hat{\mbf{p}}^{\intercal} = \left( \hat{\mbf{p}}^{\intercal}_{S,AA},\hat{\mbf{p}}^{\intercal}_{X,AA},\mbf{0},\mbf{0},\mbf{0},\mbf{0} \right)$ into the right side of Eq(A-46) so that only terms with $j=1$ and $j=2$ are nonzero, yielding

\begin{align*}
	\frac{1}{\lambda_{AA}}(\hat{\mbf{p}}^{\intercal} \otimes \mbf{I}_{2 \omega g}) \left. \frac{ \partial \text{vec}\mbf{A}}{\partial \tilde{\mbf{p}}^{\intercal}} \right|_{\hat{\mbf{p}}} &= \frac{1}{\lambda_{AA}} \sum^{6}_{i=1} \big( \hat{\mbf{p}}^{\intercal}_{S,AA} \otimes (\mbf{e}_{i} \otimes \mbf{I}_{\omega}) \big) \left. \frac{ \partial \text{vec}\mbf{A}_{i,1}}{\partial \tilde{\mbf{p}}^{\intercal}} \right|_{\hat{\mbf{p}}} \\
		&+ \frac{1}{\lambda_{AA}} \sum^{6}_{i=1} \big( \hat{\mbf{p}}^{\intercal}_{X,AA} \otimes (\mbf{e}_{i} \otimes \mbf{I}_{\omega}) \big) \left. \frac{ \partial \text{vec}\mbf{A}_{i,2}}{\partial \tilde{\mbf{p}}^{\intercal}} \right|_{\hat{\mbf{p}}} \numberthis
\end{align*}

\noindent Selfing does not depend on the frequency vector, and therefore none of the $\mbf{A}_{1,i}$ are a function of the frequency vector $\mbf{p}$,

\begin{equation}
	\left. \frac{ \partial \text{vec}\mbf{A}_{1,i}}{\partial \tilde{\mbf{p}}^{\intercal}} \right|_{\hat{\mbf{p}}} = 0,\,\text{for all }i. 
\end{equation}
